---
title: "marvel_analysis"
author: "aswanth"
date: "2024-03-05"
output: html_document
---

## R Markdown
### Marvel analysis
In the given marvel data table contains movie name, released date, budget,four 
types of box office collection, four different ratings, Production company etc.


*Setting up necessary packages for current environment.*

```{r}
library(tidyverse)
library(ggplot2)
library(janitor)
library(dplyr)
library(readr)
```



**Import marvel data frame.**

```{r}
marvel_data <-read_csv("Data/marvel_box_office.csv")
```



**data frame details.**

```{r}
glimpse(marvel_data)
```



*converting all variable names to standard format*

```{r}
marvel_data <- clean_names(marvel_data)
```



```{r}
head(marvel_data)
```



**Number of movies released in each production company**
```{r}
marvel_data |>
  ggplot(aes(x = ownership))+
  geom_bar(aes(fill = ownership))
```



**Number of movies in each phase**
```{r}
ggplot(marvel_data, aes(x = phase))+
  geom_bar(aes(fill = phase))
```



**Number of movies released in each year and month**
```{r}
marvel_data |>
  ggplot(aes(x = release_year, fill = ownership))+
  geom_bar()
```



```{r}
marvel_data |>
  count(release_month, sort = TRUE)

marvel_data |>
  ggplot(aes(x = release_month))+
  geom_bar(aes(fill = ownership),position = "dodge")+
  theme(axis.text.x = element_text(angle = 45))
```



**Total budget and world wide box office collection for movies**
**that released in each year**
```{r}
marvel_data |>
  group_by(release_year)|>
  summarise(total_budget = sum(budget),
            total_collction_worldwide = sum(worldwide_box_office))|>
  ggplot(aes(x = release_year))+
  geom_col(aes(y = total_budget, fill = release_year))+
  geom_line(aes(y = total_collction_worldwide))+
  labs(y = "budget and world wide collection")
```



**relationship between budget and worldwide collection of each movies**

```{r}
 marvel_data |>
   arrange(release_year) |>
   ggplot(aes(x = budget, y = worldwide_box_office, color = release_year))+
   geom_point(position = "jitter")+
   facet_wrap(~phase)
```



**movie which have highest and lowest budget**

```{r}
marvel_data |>
  slice_max(budget)
```



```{r}
marvel_data |>
  slice_min(budget)
```



**Movies that have highest and lowest international collection in each year**

```{r}
marvel_max <- marvel_data |>
  group_by(release_year) |>
  slice_max(international_box_office) |>
  select(movie, release_year, international_box_office, budget)|>
  arrange(release_year)
```



```{r}
marvel_min <- marvel_data |>
  group_by(release_year)|>
  slice_min(international_box_office) |>
  select(movie, release_year, international_box_office, budget)
```



```{r}
ggplot()+
  geom_col(data = marvel_max,
           aes(x = release_year, y = international_box_office), fill = "blue")+
  geom_col(data = marvel_min, 
           aes(x = release_year, y = international_box_office), fill = "orange")
```



**total box office collection and budget in each year**

```{r}
mcu_collect <- marvel_data |>
  group_by(release_year, ownership) |>
  summarise(across(c(domestic_box_office, inflation_adjusted_domestic, 
              international_box_office, inflation_adjusted_international, 
              worldwide_box_office, inflation_adjusted_worldwide, 
              opening_weekend, inflation_adjusted_opening_weekend, 
              budget, inflation_adjusted_budget),sum),
            .groups = 'drop')
```



```{r}
head(mcu_collect)
```



**domestic, international, world wide and opening weekend box office collecton**
**in each year for every company**

```{r}
mcu_collect |>
  ggplot(aes(x = release_year))+
  geom_line(aes(y = domestic_box_office),color = "green")+
  geom_line(aes(y = international_box_office), color = "red")+
  geom_line(aes(y = worldwide_box_office), color = "black")+
  geom_line(aes(y = opening_weekend), color = "blue")+
  facet_wrap(~ownership)
```



**Budget Vs imdb score**

```{r}
 marvel_data |>
   ggplot(aes(x = im_db_score, y = budget))+
   geom_point(position = "jitter", color = "blue")+
   facet_wrap(~ownership)
```



**world wide box office collection Vs imdb score**

```{r}
marvel_data |>
   ggplot(aes(x = im_db_score, y = worldwide_box_office))+
   geom_point(position = "jitter")+
   facet_wrap(~ownership)
```



**international box office collection Vs imdb score**

```{r}
marvel_data |>
   ggplot(aes(x = im_db_score, y = international_box_office))+
   geom_point(color = "blue", position = "jitter")+
   facet_wrap(~ownership)
```



**finding the mean of all ratings**

```{r}
imdb_mean <- mean(marvel_data$im_db_score)
meta_mean <- mean(marvel_data$meta_score)
tomato_mean <- mean(marvel_data$tomatometer)
rotten_mean <- mean(marvel_data$rotten_tomato_audience_score)
```



**movies which is higher or lower of each ratings**

```{r}
marvel_ratings <- marvel_data |>
   mutate(imdb_rate = ifelse(im_db_score > imdb_mean, "above_mean", "below_mean"))|>
   mutate(meta_rate = ifelse(meta_score > meta_mean, "above_mean","below_mean"))|>
   mutate(tomato_rate = ifelse(tomatometer > tomato_mean, "above_mean","below_mean"))|>
   mutate(rotten_rate = ifelse(rotten_tomato_audience_score > rotten_mean,  
                               "above_mean","below_mean"))
```



```{r}
head(marvel_ratings)
```



**Number of movies which is higher or lower than its mean ratings.**

```{r}
marvel_ratings |>
   select(movie, release_year, ownership, imdb_rate,meta_rate, tomato_rate, rotten_rate)|>
   pivot_longer(
     cols = imdb_rate:rotten_rate,
     names_to = "all_ratings",
     values_to = "above_or_below"
   ) |>
   ggplot(aes(x = above_or_below))+
   geom_bar(aes(fill = all_ratings),position = "dodge") +
   facet_wrap(~ownership)
```



**Number of movies which is higher or lower than its mean ratings for all **
**box offices and ratings**

```{r}
marvel_ratings |>
   select(movie, release_year, ownership,ends_with("rate"),
          ends_with("box_office"))|>
   pivot_longer(
     cols = ends_with("box_office"),
     names_to = "box_office_type",
     values_to = "collection"
   ) |>
   pivot_longer(
     cols = imdb_rate:rotten_rate,
     names_to = "all_ratings",
     values_to = "above_or_below"
   )|>
   ggplot(aes(x = release_year, y = collection))+
   geom_line(aes(color = above_or_below), position = "jitter")+
   facet_grid(box_office_type~all_ratings)+
   theme(axis.text.x = element_text(angle = 45))
```




